Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
update knitted- filters rhs-lhs course different grade

```{r AR apriori}

@@

We generate sequence rules:
```{r cspade and rule induction, cache = F}
#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )

##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(`RHS Quality`=="fail")

##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(`RHS Quality`=="low")

SR_Grade   <- my_SR(data = sequences_Grade )

@@

SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )

```
We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL, SR_Grade,

>>>>

```{r AR apriori, cache = TRUE}

@@

We generate sequence rules:
```{r SR taken, cache = TRUE}
#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )
```

```{r SR PF, cache = TRUE}
##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(`RHS Quality`=="fail")
```

```{r SR HL, cache = TRUE}
##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(`RHS Quality`=="low")
```

```{r SR grade, cache = TRUE}
SR_Grade   <- my_SR(data = sequences_Grade )
```

```{r SR grade exp, cache = TRUE}
#Grades filter 
SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade ) %>%
  filter(!`LHS Course ID`==`RHS Course ID`)
```

```{r cspade and rule induction, cache = F}

@@

We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL, SR_Grade,
